---
title: "Proposal title"
subtitle: "Proposal"
author: 
  - name: "Team Name - Team member 1, Team member 2,..."
    affiliations:
      - name: "School of Information, University of Arizona"
description: "Project description"
format:
  html:
    code-tools: true
    code-overflow: wrap
    code-line-numbers: true
    embed-resources: true
editor: visual
code-annotations: hover
execute:
  warning: false
---

```{r}
#| label: load-pkgs
#| message: false
library(tidyverse)
```
## Introduction 

Our project leverages a comprehensive COVID-19 dataset from Kaggle to unlock insights into the pandemic's dynamics through advanced data visualization. By analyzing case counts, recovery rates, mortality, and vaccination data, we aim to reveal trends and correlations across different regions and periods. This endeavor transcends academic boundaries, aiming to provide actionable insights for policymakers and the public. Through our analysis, we aspire to transform complex data into clear, insightful narratives, aiding in the informed response to this global health crisis.

## Dataset
```{r}
#| label: load-dataset
#| message: false

day_wise_data <- read_csv("./data/day_wise.csv")
country_wise_latest_data <- read_csv("./data/country_wise_latest.csv")
vaccination_data <- read_csv("./data/country_vaccinations.csv")


glimpse(day_wise_data)
glimpse(country_wise_latest_data)
glimpse(vaccination_data)
```

## Description

The datasets for this project were sourced from a comprehensive `Kaggle collection` maintained by "imdevskp," focusing on various aspects of the COVID-19 pandemic. These include day-wise global statistics, country-wise latest data, detailed data grouped by country and date, and USA-specific county-wise data. Each dataset provides a range of metrics such as case counts, deaths, recoveries, and vaccinations, enabling a multifaceted analysis of the pandemic. 

-  The choice of these datasets was motivated by their depth, regular updates, and the potential insights they offer into the global and localized impacts of COVID-19.

#### [Dataset Source](https://www.kaggle.com/datasets/imdevskp/corona-virus-report?resource=download&select=country_wise_latest.csv)

## Questions

### Question 1
How has the COVID-19 pandemic trended globally over time, and what correlations can be observed between different pandemic metrics (like cases and recoveries)?

### Question 2
What is the relationship between total vaccinations and the reduction in active COVID-19 cases across different countries?


## Analysis plan

### For the first question:

Dataset: We will utilize the `day_wise_data` dataset, which provides daily global statistics on COVID-19.

**Focus**: Our analysis will concentrate on total cases, recoveries, and deaths, offering a comprehensive view of the pandemic's evolution over time.

**Visualizations:**

-  Time-series plots will be our primary tool, showcasing how each of these metrics has evolved daily. We will create separate line graphs for total cases, recoveries, and deaths, as well as a combined graph to facilitate direct comparisons.

-  To further understand the dynamics, we'll calculate and plot the daily percentage changes for each metric, providing insights into the pandemic's velocity at different stages.
Correlation coefficients between the different metrics will be calculated and visualized using scatter plots, helping us understand the relationships between cases, recoveries, and deaths over time.

**Additional Analysis:**

-  We will perform a rolling average analysis to smooth out the data, making trends more discernible.

-  Anomaly detection might be applied to identify any unusual changes in the data, which could signify important events or turning points in the pandemic's course.

### For the second question:

**Dataset Utilization**: We will employ the `usa_county_wise_data` dataset, which is rich in localized COVID-19 data for the United States, encompassing each county's case and vaccination figures. And `vaccination` dataset provides the details of vaccian all over the world.


**Primary Focus**: Our primary objective is to dissect and understand the spatial distribution and temporal evolution of COVID-19 cases alongside vaccination rates across the U.S. counties, aiming to identify any significant geographical patterns or correlations.

**Visualizations**

-  Choropleth Maps: We will craft choropleth maps to visually represent the density or intensity of COVID-19 cases and vaccination rates across U.S. counties. This will enable a straightforward interpretation of regional variances and trends.

-  Bubble Maps: To enhance our spatial analysis, bubble maps will be constructed where each bubble's size indicates either the number of cases or vaccination rates in counties, offering a dual perspective on the pandemic's magnitude and the vaccination effort.

-  Time-Lapse Visualizations: Implementing time-lapse maps will allow us to observe and analyze the progression of the pandemic and vaccination rollout over time, providing dynamic insights into how the situation has evolved across different regions.


